---
title: "Hw01"
output: html_document
---
```{r}
library(tidyverse)
```


# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
penguins = janitor::clean_names(penguins)
mean_flipper = mean(pull(penguins, flipper_length_mm))
```

Here is a summary of the penguin dataset 
`r skimr::skim(penguins)`

Variable names include `r names(penguins)`

The size of the penguins dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean_flipper`


Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r}

ggplot(penguins, aes(x = bill_length_mm,  y = flipper_length_mm, color = species))+geom_point()
ggsave("hw01_scatterplot.png")

```

# Problem 2
```{r}
prob2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("cake","cookies", "crepes", "croissants", "creampuff", "cannolli", "cheesecake", "cupcake", "crumble", "cobbler" ),
  vec_factor = factor(c("good", "better", "best", "good", "better", "best", "good", "better", "best", "best"))

)

mean_norm_samp = mean(pull(prob2_df, norm_samp))
mean_samp_pos = mean(pull(prob2_df, norm_samp_pos))
mean_vec_char = mean(pull(prob2_df, vec_char))
mean_vec_factor = mean(pull(prob2_df, vec_factor))


```

The mean for the sample is `r mean_norm_samp`. This works because it is a numerical variable. 
The mean for the logical vector indicating whether elements of the sample are greater than 0
is `r mean_samp_pos`. This works because it is a numerical variable. 

The mean for the character vector is `r mean_vec_char`. This does not works because it is a chracter variable. 
The mean for the factor vector is `r mean_vec_factor`. This does not works because it is a character/factor variable. 








