---
title: "Hw01"
output: html_document
author: "Dominique Tzou"
date: 2026-09-26
---

```{r}
library(tidyverse) #loading in tidyverse, to use the pull function later
```


# Problem 1

```{r penguins_dataset}
data("penguins", package = "palmerpenguins") #Loading in penguins dataset
penguins = janitor::clean_names(penguins) #cleaning names
```

## Summary of the penguin dataset and variables
`r skimr::skim(penguins)`


Some additional details
* Variables: Variable names include `r names(penguins)`

* Years: The data spans from Year `r min(pull(penguins, year))` to `r max(pull(penguins, year))`

* Size: The size of the penguins dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE ), digits = 2)` mm.


### Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r scatterplot}

ggplot(penguins, aes(x = bill_length_mm,  y = flipper_length_mm, color = species))+geom_point()
ggsave("hw01_scatterplot.png")

```

# Problem 2

Creating a dataframe
```{r dateframe}
# setting seed to ensure reproducibility
set.seed(4321)

prob2_df = tibble(
  norm_samp = rnorm(10),#a random sample of size 10 from a standard Normal distribution
  norm_samp_pos = norm_samp > 0, #a logical vector indicating whether elements of the sample are greater than 0
  vec_char = c("cake","cookies", "crepes", "croissants", "creampuff", "cannolli", "cheesecake", "cupcake", "crumble", "cobbler" ), #a character vector of length 10 desserts
  vec_factor = factor(c("good", "better", "best", "good", "better", "best", "good", "better", "best", "best")) #a factor vector of length 10, with 3 different factor “levels: good, better, best”

)
#taking the mean of each 4 variables
mean_norm_samp = mean(pull(prob2_df, norm_samp))
mean_samp_pos = mean(pull(prob2_df, norm_samp_pos))
mean_vec_char = mean(pull(prob2_df, vec_char))
mean_vec_factor = mean(pull(prob2_df, vec_factor))


```

### Mean results of variables 

The mean for the sample is `r round(mean_norm_samp, digits = 4)`. This works because it is a numerical variable. 

The mean for the logical vector indicating whether elements of the sample are greater than 0
is `r mean_samp_pos`. This works because it is a numerical variable. 

The mean for the character vector is `r mean_vec_char`. This does not works because it is a character variable. 

The mean for the factor vector is `r mean_vec_factor`. This does not works because it is a character/factor variable. 



### Attempting to convert character variables into numeric

```{r , numeric_conversion, results = 'hide', warning = FALSE}
as.numeric(pull(prob2_df,norm_samp_pos))
as.numeric(pull(prob2_df,vec_char))
as.numeric(pull(prob2_df,vec_factor))

```

When applying the as.numeric function to the logical and factor variables, their output categories (often repeated in the dataframe) are converted/designated to numerical values, so that a mean can be taken. But when as.numeric function is applied to the character variable, it is unsuccessful, but of its unique character variables. A mean cannot be calculated.



